Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-10-31 WSSSPE4_report/WSSSPE4_report.tex
added Kyle for lightning talk todo
adding initial guess for sections and section leads

@@

\todo{go through subsections that have both content here and appendix, and add pointer from text in the subsection here to the corresponding appendix} \todo{though think about if an appendix is the right thing if we decide to publish in JORS again}

>>>>

\note{Kyle Niemeyer will write this}

@@

Sections: \todo{copy wg\_open\_research\_index for each, add input command for each new file}

\begin{itemize}
\item Verifying best practices \& metrics for sustainable software [Ray Idaszak]
\item Software Sustainability Alliance [Neil \& Jean]
\item Scientific Software Prototyping Infrastructure (S2PI) [Santiago Nunez-Corrales] 
\item CodeMeta working group [Alice Allen]
\item White paper on developing sustainable software [Sandra Gesing]
\item Social Science of Scientific Software [Stuart Geiger]
\item Software development best practices [Jonah Miller]
\item Meaningful metrics for sustainable software [Emily Chen]
\item Coordinating access to CI for research software [Mark Abraham]
\item Software engineering processes tailed for research software [Anshu Dubey]
\item Open research index [Dan]
\item Letters of evaluation for computational scientists [Wolfgang Bangerth]
\end{itemize}
